---
title: "simpleRegress"
author: "Sylvia Rodriguez"
date: "October 26, 2021"
output: html_document
---


## make a simple regression model


```{r}
fullup <- lm(LENGTH~ .,data=BEARS)
summary.lm(fullup)
```

This chart gives us the residuals and coefficients of all parts, as well as the P value at the end which is < 2.2e-16. Because the formula only called for "length" of bears and not a specific part (e.g. neck, head, etc) we are given the totals of every part.

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=BEARS)
plot(LENGTH~NECK,data=BEARS)
abline(simp)
summary.lm(simp)
```

This first model is a much clearer way to see the length of the bears' necks. The length continues to increase in a linear motion. 

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

